\bf A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes

### 2017-10-06 paper/paper.tex
Fix notation in replicate data method

An obstacle remains, in that the censoring mechanism itself is not fully observed. Our admittedly simple approach is to assume that failed units would have been the censored had they survived until the latest censoring or failure time for that drive model. We generated 19 replicates for each drive model. This gives a 1/20 chance under the hypothesis of no difference that the Kaplan-Meier estimate based on the observed data would be ``most extreme" relative all the replicated  from the those one and is not too many so as to produce an overly cluttered plot. Our method for generating replicate data sets, $y_{rep,g}^{(s)}$, $s = 1 \dots 19$, for each drive-model $g=1,\ldots,44$, is as follows:
\begin{enumerate}
\item Simulate $\tilde{t}_{rep,g,i}^{(s)} \sim \op{GLFP}(\pi_{g}^{(s)},\mu_1^{(s)},\sigma_1^{(s)},\mu_{2g}^{(s)}, \sigma_{2g}^{(s)})$ where each set of parameters, \\$\left( \pi_{g}^{(s)},\mu_1^{(s)},\sigma_1^{(s)},\mu_{2g}^{(s)}, \sigma_{2g}^{(s)} \right)$, is a random draw from the full posterior distribution.
\item Repeat step 1 until $\tilde{t}_{rep,g,i} > t_{g,i}^L$.
\item If $c_{g,i}=0$, let $c_{rep,g,i}^{(s)}=\max \{t_{g,i}: i \ge 1\}$, otherwise let $c_{rep,g,i}^{(s)}=t_{g,i}$.\\
If $\tilde{t}_{rep,g,i}^{(s)}>m_{g,i}$, set $t_{rep,g,i}^{(s)}=c_{rep,g,i}^{(s)},\; c_{rep,g,i}^{(s)}=1$, otherwise set $t_{rep,g,i}^{(s)}=\tilde{t}_{rep,g,i}^{(s)},\; c_{rep,g,i}^{(s)}=0$.
\end{enumerate}

>>>>

An obstacle remains, in that the censoring mechanism itself is not fully observed. Our admittedly simple approach is to assume that failed units would have been the censored had they survived until the latest censoring or failure time for that drive model. We generated 19 replicates for each drive model. This gives a 1/20 chance under the hypothesis of no difference that the Kaplan-Meier estimate based on the observed data would be ``most extreme" relative all the replicated  from the those one and is not too many so as to produce an overly cluttered plot. Our method for generating replicate data sets, $y_{rep,g}^{(s)}$, $s = 1 \dots 19$, for each drive-model $g=1,\ldots,44$, is as follows:
\begin{enumerate}
\item Simulate $\tilde{t}_{rep,g,i}^{(s)} \sim \op{GLFP}(\pi_{g}^{(s)},\mu_1^{(s)},\sigma_1^{(s)},\mu_{2g}^{(s)}, \sigma_{2g}^{(s)})$ where each set of parameters, \\$\left( \pi_{g}^{(s)},\mu_1^{(s)},\sigma_1^{(s)},\mu_{2g}^{(s)}, \sigma_{2g}^{(s)} \right)$, is a random draw from the full posterior distribution.
\item Repeat step 1 until $\tilde{t}_{rep,g,i} > t_{g,i}^L$.
\item Set $d_{g,i}^{(s)}= \begin{cases} \max \{t_{g,i}: i \ge 1\}, & \mbox{ if }c_{g,i}=0\\
t_{g,i}, & \mbox{ if }c_{g, i}=1. \end{cases}$\\
Lastly, set $(t_{rep,g,i}^{(s)},c_{rep,g,i}^{(s)}) = \begin{cases}
  (d_{g,i}^{(s)},1), & \mbox{ if } \tilde{t}_{rep,g,i}^{(s)}>d_{g,i}^{(s)}\\
  (\tilde{t}_{rep,g,i}^{(s)},0), & \mbox{ if }\tilde{t}_{rep,g,i}^{(s)} \le d_{g,i}^{(s)}.
\end{cases}$
\end{enumerate}
